---
title: "simpleRegress"
author: "Keren Gonzalez"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```



## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE, interval= "prediction")
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

Informally, this model seems to be a better model than the first model comparing HEAD and LENGTH. This model seems better because the residual standard error is smaller and the adjusted R-square is explaining more of error than the other model.

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```
Compared to the first model of NECK and LENGTH, there is a similar residual standard error and adjusted R-squared. This means both models are about the same and not as effective as comparing CHEST and LENGTH.

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

This model seems to be much better than the previous ones because the residual standard error is smaller and the adjusted R-squared is higher.

In conclusion, we looked for a model that would be best for predicting the length of the bear based on a different variable in our data set. At first we tested Neck which gave us a residual standard error of 5.376 and an adjusted R-squared of 0.7476. When we tested Weight, we got similar results as when we tested Neck. We tested Chest size and Head length, and both were better models for predicting the length of the bear. However, choosing Head length(HEADLEN) yielded the best model as it had the lowest error out of all models(4.235) and a higher adjusted r-squared(0.8434).


